Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-25 WRITEUP/ms.tex
fig caption

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar on the right.
We also plot gas-only $\alpha_{\rm vir}$ (orange star symbols), which is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs,
since they are gas-dominated (see \Fig{stellarRatio16}).
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
since they are gas-dominated (see \Fig{stellarRatio16}). 
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
and \citet{Kauffmann17b}.
\label{fig:larsons_single}}
\end{figure*}
